Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-22 methods_paper/fabl-paper.tex
working on intro.

The Fellegi-Sunter method and its extensions are widely popular mainly due to its simplicity and computational scalability. Despite this, like any method, it has limitations, that are well known in the literature. Specifically, the assumption of no duplications within a database implies a maximum one-to-one constraint. That is, a record from one database ban be linked with only one record in the other database. Modern methods of Fellegi-Sunter either ignore this restriction \citep{Winkler1988, belin_1995, larsen_2001}, include this as a post-processing step \citep{Jaro1989}, or include it directly in the modeling framework \citep{sadinle_bayesian_2017}. It is important to note that \cite{fellegi_theory_1969} ignored this restriction as well. In practice, it seems that one should either directly include it in the modeling framework or correct for this in a post-processing step.

To our knowledge, \cite{sadinle_bayesian_2017} was the first to propose correcting the Fellegi and Sunter model for the one-to-one constraint. Specifically, the authors propose a Bayesian variant of the original model. This satisfies two goals. First, it allows one to quantify uncertainty regarding match or non-match status. In addition, posterior distributions are readily available to help estimate point estimates of interest (and quantity such estimates). Second, under the Bayesian paradigm, the one-to-one matching constraint is easily imbedded. The downside to this constraint is an added computational cost. Our goal is proposing a model in the spirit of \cite{sadinle_bayesian_2017}, which scales beyond the original proposed model, without sacrificing much in the way of accuracy or precision of the resulting estimates.

@@

Then mention related work.

@@

\begin{enumerate}
\item Let's re-visit the case study of Sadinle. Lay this out and the importance of it. 
\item Next, let's briefly review the landscape of the literature. 
\item State Brian's contributions. 
\item Then write a section on related work. 
\item Then write a section regarding the layout of the paper.
\end{enumerate}

>>>>

The Fellegi-Sunter method and its extensions are widely popular mainly due to its simplicity and computational scalability. Despite this, like any method, it has limitations, that are well known in the literature. Specifically, the assumption of no duplications within a database implies a maximum one-to-one constraint. That is, a record from one database can be linked with only one record in the other database. Modern methods of Fellegi-Sunter either ignore this restriction \citep{Winkler1988, belin_1995, larsen_2001}, include this as a post-processing step \citep{Jaro1989}, or include it directly in the modeling framework \citep{sadinle_bayesian_2017}. It is important to note that \cite{fellegi_theory_1969} ignored this restriction as well. In practice, it seems that one should either directly include it in the modeling framework or correct for this in a post-processing step.

To our knowledge, \cite{sadinle_bayesian_2017} was the first to propose correcting the Fellegi and Sunter model for the one-to-one constraint. Specifically, the authors propose a Bayesian variant of the original model that satisfies two goals. First, it allows one to quantify uncertainty regarding match or non-match status. In addition, posterior distributions are readily available to help estimate point estimates of interest (and quantity such estimates). Second, under the Bayesian paradigm, the one-to-one matching constraint is easily imbedded. The downside to this constraint is an added computational cost. The goal of our paper is proposing an extension of \cite{sadinle_bayesian_2017} that scales to large databases, but does not compromise much in terms of accuracy on the original case study considered by the author.

\textbf{Our Contributions}

@@

@@

%\begin{enumerate}
%\item Let's re-visit the case study of Sadinle. Lay this out and the importance of it. 
%\item Next, let's briefly review the landscape of the literature. 
%\item State Brian's contributions. 
%\item Then write a section on related work. 
%\item Then write a section regarding the layout of the paper.
%\end{enumerate}
